---
title: "Financial Informatics"
output:
  html_document:
    df_print: paged
---
## Chap2. W2-2: Investment Return

1. investment Holding period return

$$R_h = \frac{(Gain\ from\ Investment\ -\ Cost\ for \ Investment) }{Cost\ for \ Investment}$$
```{r}
dat <- data.frame( horizon = c(0.5, 1, 25), # holding years 
                   cost = c(2063.11, 2058.9, 459.27), # investment cost
                   gain = c(2043.94, 2043.94, 2043.94)) # investment gain

dat["Holding Period Return"] <- round((dat$gain - dat$cost) / dat$cost * 100,2)
dat
```

2. Compound Return: return on return
  - $$P(1+i)^n\\\ P= original\ investment,\\ i=annual\ return,\\ n= number\ of\ years\ in\ investment$$

3. Annualized Return:
  - assumption: the interest rate for certain period will remain same for the rest of assuming period
$$R = (1+R_H)^\frac{1}{n}-1\\ \  \\ R_H: holding\ period\ return\\ n: the\ number\ of\ years\ the investment\ was\ held\\$$
```{r}
dat["Annaulized Return"] <- apply(dat,1,function(x) (1+x[4])^(1/x[1])-1)
dat
```

4. Risk Premium
  - Risk free return (R~f~): Theoretical rate of return with no risk
  - Risk Premium: the return in excess of the risk free return at investment is expected to yield
$$ Risk\ Premium = E(R) - R_f$$

5. Expected Return: the amount investor would anticipate receiving from investment considering various scenarios.
  * Arithmetic mean
    + P(s) : probability of status s
    + E(R~s~) : expected return under status s

$$ E(R) = \sum_{s=1}^{n}P(s)\times E(R_s)$$

```{r}
dat2 <- data.frame(c("Excellent", "Good", "Poor", "Terrible"),
                   c(0.3, 0.2, 0.4, 0.1),
                   c(20, 10, -5, -40))

colnames(dat2) <- c("Status", "P(s)", "E(R_s)")
dat2

dat2[5,3] <- sum(dat2[2]*dat2[3])
dat2[5,2] <- "Expected Return"
dat2
```

6. 
```{r}

```

